Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-04 ProbabilisticCoherence.tex
Abstract added

\begin{abstract}
  TBC
\end{abstract}

%
%\section{Introduction}\label{sec:intro}
%Sketch narrative to tell
%\begin{itemize}
%	\item Coherence is important in point forecasting to
%	\begin{itemize}
%		\item Align decisions
%		\item Improve forecasts
%	\end{itemize}
%	\item We propose a geometric interpretation via linear transformations including special case of projections.
%	\item These nest existing methods but the interpretation has advantages 
%	\begin{itemize}
%		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
%		\item Most importantly generalises to probabilistic forecasting.
%	\end{itemize}
%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
%    \item Discuss evaluation of forecasts
%    \begin{itemize}
%    	\item Log score improper when coherent v incoherent
%    	\item Energy score cn be used instead
%    	\item Discuss scores for coherent v coherent.
%    \end{itemize}
%    \item Finally evidence MinT is best from simulation
%\end{itemize}

>>>>

\begin{abstract}
  The process by which forecasts are adjusted to ensure coherence to aggregation constraints that hold for real data - known as forecast reconiliation - is extended from the point forecasts to probabilistic forecasts.  This is achieved by redefining many concepts from the existing literature in terms of linear mappings in general, and projections more specifically.  New theorems establish that linear reconciliation can recover the true predictive distribution in the elliptical case as well as general conditions for when this can be achieved via projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.  Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.  Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}

%
\section{Introduction}\label{sec:intro}
%Sketch narrative to tell
%\begin{itemize}
%	\item Coherence is important in point forecasting to
%	\begin{itemize}
%		\item Align decisions
%		\item Improve forecasts
%	\end{itemize}
%	\item We propose a geometric interpretation via linear transformations including special case of projections.
%	\item These nest existing methods but the interpretation has advantages 
%	\begin{itemize}
%		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
%		\item Most importantly generalises to probabilistic forecasting.
%	\end{itemize}
%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
%    \item Discuss evaluation of forecasts
%    \begin{itemize}
%    	\item Log score improper when coherent v incoherent
%    	\item Energy score cn be used instead
%    	\item Discuss scores for coherent v coherent.
%    \end{itemize}
%    \item Finally evidence MinT is best from simulation
%\end{itemize}
